### 2020-01-18 nlp_models.tex
more NLP text

\begin{figure}
    \centering
    \subfigure[Power Law Exponent $\alpha$]{
        \includegraphics[width=5cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha-hist}
       }
    \qquad
    \subfigure[log Spectral Norm $\log\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=5cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm-hist}
       }

@@

    \subfigure[Power Law Exponent $\alpha$]{
        \includegraphics[width=4.5cm]{img/GPT-alpha-depth.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[log Spectral Norm $\log\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT-snorm-depth.png}
        \label{fig:gpt-snorm-layer}
    }
    \qquad
    \subfigure[log Alpha-Norm $\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT-pnorm-depth.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{GPT2: small, medium, large, extra-large}

Figure \ref{fig:gpt-alpha-layers} ...

For this series of GPT2 models, the average $\alpha$ still decreases with increasing model size,
althogh, the differences are less noticible than between the GPT and GPT2 models.
Unlike GPT, however, the Layer (log) Spectral Norms $\log\vert\mathbf{W}\Vert_{\infty}$ 
and (log) Alpha-Norms $\log\vert\mathbf{W}\Vert_{\alpha}^{\alpha}$
 behave  as expected for GPT2 layers, with the larger models  consistently having  smaller norms.

@@

    \subfigure[Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[log Spectral Norm $\log\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2*_all_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[log Alpha-Norm $\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_logpnorm_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.  *Note: the log spectral norms (b) histogram omits the first 2 layers, corresponding to the embedding layer, which are normalized differently and have anamolously large values.}
    \label{fig:gpt-alpha-layers}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfigure[Power Law Exponent $(\alpha)$]{
        \includegraphics[width=5cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha-hist}
       }
    \qquad
    \subfigure[log Spectral Norm $(\log\Vert\mathbf{W}\Vert_{\infty})$]{
        \includegraphics[width=5cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm-hist}
       }

@@

    \subfigure[Power Law Exponent $(\alpha)$]{
        \includegraphics[width=4.5cm]{img/GPT-alpha-depth.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[log Spectral Norm $(\log\Vert\mathbf{W}\Vert_{\infty})$]{
        \includegraphics[width=4.5cm]{img/GPT-snorm-depth.png}
        \label{fig:gpt-snorm-layer}
    }
    \qquad
    \subfigure[log Alpha-Norm $(\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha})$]{
        \includegraphics[width=4.5cm]{img/GPT-pnorm-depth.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Correlation Flow and Spectral Norm for OpenAI GPT and GPT2   }
    \label{fig:gpt-alpha-layers}
\end{figure}

\paragraph{GPT2: small, medium, large, xl}

We now look across the series of increasingly improving GPT2 models, examining both our
PL exponent $\alpha$, as well as the various Norm metrics.
As we move from small to xl, both the PL exponents $\alpha$, and the peak of distribtion of
log Norm metrics shifts from larger to smaller values. 
Figure \ref{fig:gpt2-histograms} shows the histograms over the layer weight matrics
for fitted $\alpha$, and the log Spectral Norm
 $\log\Vert\mathbf{W}\Vert_{\infty}$  
and log Alpha-Norm
 $\log\Vert\mathbf{W}\Vert_{\alpha}^{\alpha}$ 
metrics.

We see that the average $\alpha$ decreases with increasing model size,
althogh, the differences are less noticible between GTP2 mkodels than between the GPT and GPT2 models.
Unlike GPT, however, the Layer (log) Spectral Norms $\log\vert\mathbf{W}\Vert_{\infty}$ 
and (log) Alpha-Norms $\log\vert\mathbf{W}\Vert_{\alpha}^{\alpha}$
behave more as expected for GPT2 layers, with the larger models  consistently having  smaller norms. 
Likewise, Figure \ref{fig:gpt2-snorm-hist} shows decreasing average log Spectral Norms
with the larger models.   As we have seen in the trends of other well trained models.

We do notice, however, that while the peaks of the $\alpha$ is getting smaller, towards $2.0$,
the tails of the distribution shifts right, with larger GPT2 models having more
usually large $\alpha$.  We suspect this indicates that these larger GPT2 models are 
overparameterized and/or not yet fully optimized and require datasets even larger
than the recent XL $1.5B$ release\cite{gpt2-xl}.

@@

    \subfigure[Power Law Exponent $(\alpha)$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt2-alpha-hist}
    }
    \qquad
    \subfigure[log Spectral Norm $(\log\Vert\mathbf{W}\Vert_{\infty})$]{
        \includegraphics[width=4.5cm]{img/GPT2*_all_spectralnorm_hist.png}
        \label{fig:gpt2-snorm-hist}
    }
    \qquad
    \subfigure[log Alpha-Norm $(\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha})$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_logpnorm_hist.png}
        \label{fig:gpt2-pnorm-hist}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.  *Note: the log spectral norms (b) histogram omits the first 2 layers, corresponding to the embedding layer, which are normalized differently and have anamolously large values.}
    \label{fig:gpt2-histograms}
\end{figure}
